Lattice Boltzmann simulations of magnetically responsive\\ anisotropic particle stabilized emulsions

### 2025-03-05 chapters/introduction.tex
Changes 1. Reworded introduction and lit review and addressed grammar and vocab issues 2. Fixed some referencing problems in the document 3. Fleshed out introduction in paper 2 4. Added sections for results in paper 3

Porous materials are defined as materials that contain pores or voids within their structure where no material is present. 
Homogeneous materials in contrast have a uniform structure with no pores. These pores vary in shape and distribution, with materials 
being categorized by pore size per IUPAC as $(L)$ as microporous $(L < 2nm)$, mesoporous $(2nm < L < 50nm)$ and macroporous materials 
$(50nm < L)$. \cite{sing_reporting_1985} The presence of these pores increases the surface area to volume 
ratio of porous materials compared to their homogeneous counterparts. A common experimental technique used to estimate the surface area 
of a porous material derived from Brunauer-Emmett-Teller(BET) theory shows that porous materials can have surface areas more than a 
hundred times larger than homogenous materials, dependent upon the pore size and pore size distribution. \cite{shimizu_surface_2022}

In addition to the pore size and its distribution within the material, the arrangement of pores within the material contribute to the 
performance of the synthesized material, commonly measured using the tortuosity. Tortuosity here is defined as the path length between 
two points divided by the euclidean length between those points. A tortuosity larger than one implies that the path length is longer 
than the euclidean length, and vice versa if the tortuosity if less than one. Highlighting the confluence of these factors are the 
large variety of tailored microstructures for various applications. Each of the specified pore length scales have their unique uses, 
such as microporous materials being used as zeolites and photonic bandgap materials while macroporous materials facilitate greater 
transport properties, suitable in applications such as battery electrodes and drug delivery systems. \cite{chen_tortuosity_2020, 
ebner_tortuosity_2014} This increased surface area to volume ratio enhances the properties of the base material in applications such 
as catalysis, battery electrodes and drug delivery systems among many more making them valuable microstructures. 
\cite{cha_bicontinuous_2019, samdani_bicontinuous_2017, thorson_bijel-templated_2019, zhao_highly_2014}

@@

Conventionally, porous materials have been synthesized through solvothermal synthesis or pyrolysis used in the synthesis of zeolites and 
activated carbon respectively. With more targeted applications of porous materials, synthesis techniques such as sol-gel synthesis, 
freeze drying and various forms of templating have been utilized to synthesize porous materials from length scales of $10^{-9}m$ to 
$10^{-3}m$. \cite{stein_morphological_2008, ray_comprehensive_2016, cervellere_mesoscopic_2019, garcia-bennett_unique_2020, zhang_emulsion_2019, 
alves-rosa_design_2013} Industry has also taken up techniques such as electrospinning to generate non woven fibers, used in membrane synthesis. 
Templating techniques in particular offer access to various pore length scales, bottom up synthesis and functionality through leveraging various 
physical phenomena. Colloidal templating works through the close packing of particles. Surfactant and polymer templating work through the 
assembly of macromolecules into their equilibrium configurations. Emulsion templating utilizes the phase separation of partially miscible 
liquids to form the pore structure of a porous material.

Emulsion templating offers access to a large length scale of tunable pore sizes, continuous production through microfluidic junctions or 
other flow media, functionalization through the addition of additives or stabilizers, scope of accessible microstructures and mild synthesis 
conditions. It can further be extended to include heirarchical porosity, further enhancing its utility and fabricated material properties. 
\cite{yang_hierarchically_2017, thompson_hierarchically_2019, wang_morphology_2023} Figure \ref{fig:bijel_template} demonstrates how emulsion 
templating allows bottom up synthesis of hierarchically porous materials, although other examples do exist. 
\cite{garcia_scalable_2019, santiago_cordoba_aerobijels_2020, thorson_bijel-templated_2019, lu_controllable_2020, wang_morphology_2023}

@@

One such emulsion microstructure of interest is the bicontinuous interfacially jammed emulsion gel(bijel). 
\cite{stratford_colloidal_2005, herzig_bicontinuous_2007, lee_bicontinuous_2010} Bijels are made by arresting the spinodal decomposition of 
partially miscible liquids, caused by particles adsorbing on the interface and jamming as the cross sectional area of the particles match that 
of the interface, summarized in Figure \ref{fig:bijel_coarsen}. Bijels are of interest due to their co-continuous, tortuous microstructure which 
represent excellent fits for several porous material applications.

Bijels were discovered in simulations in 2005 and experimentally realized in 2007 when a mixture of water and 2-6-lutidine mixed with 
surface modified silica nanoparticles underwent thermally induced spinodal decomposition. \cite{stratford_colloidal_2005, herzig_bicontinuous_2007}
Since then, multiple other casting mixtures and particle chemistry's have been used to fabricate bijels using Thermally Induced Spinodal 
Decomposition (TIPS). \cite{lee_bicontinuous_2010, bai_dynamics_2015} More recently, techniques such as Solvent Transfer Induced Phase 
Separation (STrIPS), Vapor Induced Phase Separation (VIPS), Non-solvent Induced Phase Separation (NIPS), homogenization and liquid in 
liquid printing have been utilized to fabricate bijels, demonstrating the ability for bijels to be synthesized in a continuous process, 
suitable for scale up. \cite{haase_continuous_2015, wang_scalable_2020, cai_bijels_2017, yabuno_preparation_2020, wang_bicontinuous_2023, 
amirfattahi_fabrication_2024} These techniques also offer preparation of bijels in various different shapes and form-factors for various 
uses such as fibers, coatings and capsules, seen in Figure \ref{fig:strips}. \cite{haase_continuous_2015, boakye-ansah_controlling_2020, 
kharal_hightensile_2020, wang_bicontinuous_2023}
\begin{figure}[h]
    \centering
    \includegraphics[scale = 2]{figures/literature_review/STRIPPS.jpg}
    \caption{STrIPS in action. Extrusion of the bijel casting mixture into a non-solvent bath, followed by removal of solvent from 
    the casting mixture through diffusion. Reproduced from Haase et al. 2015 under license number 5913140219015. \cite{haase_continuous_2015}}
    \label{fig:strips}
\end{figure}

However, these techniques all depend upon controlling the rate of phase separation, which involve changing the casting mixture composition to 
modify the obtained microstructure. In STrIPS, the obtained bijel microstructure is a function of the flow rate and selected co-solvent, 
selected to change the rate of phase separation. \cite{haase_continuous_2015} This affects material properties such as the mechanical 
performance of the bijel, important in fields such as catalysis where rigidity of the particle monolayer is crucial in ensuring consistent 
performance. \cite{reeves_particle-size_2015, haase_situ_2016, boakye-ansah_controlling_2020} Identification of other techniques that can 
be utilized to modify the microstructure of a bijel would enable bijels to continue using the desired composition of constituents, while 
also adding other unique properties. Stimuli response offers one such road to microstructure modification.

@@

Stimuli response based on pH, external fields and temperature have been used in past works when looking at modifying the microstructure of 
emulsion droplets for enhanced oil recovery, pharmaceutical and cell adhesion. \cite{haase_nanoparticle_2011, tham_magnetophoresis_2021, 
cui_stabilizing_2013, manfredini_limonene--water_2021}  It was shown that external fields can be used to move, control emulsion stability 
and elongate emulsion droplets. \cite{tham_magnetophoresis_2021, cui_stabilizing_2013, melle_pickering_2005} Bijels stabilized spherical 
particles under a magnetic field showed no meaningful microstructure changes. \cite{kim_bijels_2010} Bijels stabilized with spherical 
particles under an electric field showed more promise. \cite{carmack_tuning_2018} However, magnetic fields offer targeted stimuli 
response, allowing even weak fields to incite a response. Magnetic fields non-interaction in many situations offer advantages to many of 
the desired uses of bijels within pharmaceutical or bioengineering applications. \cite{vanoli_bijels_2022, thorson_bijel-templated_2019, thorson_composite_2018} 
These applications can also take advantage of in-situ microstructure modification that would enable tunable drug delivery rates, separations or
catalyst efficiency and permeability improvements in the system. Therefore, identifying schemes that allow modification of the pore size 
and tortuosity without synthesis of a new material would enhance the use case of bijels.

Anisotropic particles at interfaces have shown self assembly due to the presence of multi-polar pressure fields caused by interface deformation. 
Self assembly has also been shown for ellipsoidal particles at interfaces under magnetic fields. Ellipsoidal particles have also been shown to 
exhibit magnetic field controlled orientations at interfaces, as Bresme and Faraudo showed. \cite{bresme_orientational_2007, davies_interface_2014}
Under magnetic fields, assemblies of multiple ellipsoidal particles have been shown to have energy minima at orientations different from isolated particles,
meaning that the interface coverage of interfaces decorated with ellipsoidal particles can be varied using stimuli response. 
\cite{newton_influence_2014, newton_capillary_2018} Thus ellipsoidal particles at interfaces, whose orientations and packing can be 
controlled through external fields, offer a potential means to control the microstructure of bijels.

Bijels present a bottom up synthesis strategy for porous material templates for hard and soft material applications in a scalable and 
continuous method using STrIPS and other techniques. However, the microstructure control these techniques offer are intrinsically linked 
to the casting mixture composition. Stimuli response offers a way to modify the microstructure of bijels while still maintaining the 
various form factors these continuous synthesis techniques can output. Magnetic stimuli response has been explored in the past using bijels 
stabilized with spherical particles with little success. \cite{kim_bijels_2010}

With this background, we propose anisotropic particles as a technique to enable microstructure modification of bijels 
upon application of an external field during and after fabrication. This work seeks to identify means to control the bijel microstructure independent 
of the casting mixture composition by utilizing magnetic stimuli on bijels stabilized with magnetically responsive ellipsoidal particles. 
The proposed mechanism of microstructure modification is driven through reorientation of the particles to the applied magnetic field altering 
how the particles pack on the interface. By changing the interfacial packing of the particles, we change when the particles jam, which in turn changes 
the jamming point of the bijel. This mechanism is predicted to be effective during and after synthesis. The processability of bijels fabricated using 
this technique will also be investigated to ascertain how changes in particle packing affect the rheology of the material. An overview of three major 
research aims will be presented below.

@@

The jamming point of a bijel controls the obtained microstructure, as shown by previous work comparing the length scale of bijels synthesized 
with different particle volume fractions and particle sizes. \cite{jansen_bijels_2011, reeves_particle-size_2015} It has also been shown how magnetic fields 
can be used to enable self assembly of ansisotropic particles at interfaces and control the interfacial angle between the particle axis of symmetry and the interface. 
\cite{davies_interface_2014, davies_assembling_2014}
On a curved interface with many other particles, it is unknown how multiple particles orienting to a field and having regular structure will affect when and how the bijel 
will jam. \cite{bresme_orientational_2007, davies_interface_2014}

To assess the obtained microstructure upon application of a field during formation of the bijel, homogenous mixtures containing spherical and 
ellipsoidal particles will be subjected to field strengths above and below the critical field strength when particle orientations to the 
interface are controlled by the applied field strength, as calculated by Bresme and Faraudo for the particle aspect ratio. \cite{bresme_orientational_2007, davies_interface_201} This selection of fields 
will allow insight into the controlling mechanisms behind microstructural changes observed, allowing verification of the hypothesis and 
ascertainment where the most control over the microstructure can be exercised.

The average and directional domain sizes in addition to their relation with tortuosity will allow characterization of the microstructural properties 
of the resulting bijel. The nematic order parameter and average interfacial angle will be used to investigate how the application of the 
field affects the particle ordering to each other, and to the interface. Finally, the radial distribution function will be used to assess 
if the orientational changes expected upon field application, affects the packing of the particles on the interface.

@@

Particles on the surface of emulsion droplets have been shown to unjam and rejam into new, stable microstructures upon application of 
stimuli. \cite{cui_stabilizing_2013} Magnetic fields applied to bijels stabilized with ellipsoidal particles will facilitate unjamming and rejamming of
the particle monolayer, resulting in microstructure modification of the bijel. Due to local changes in the state of the particles, specifically the 
interfacial ordering in a specific direction and arrangement of particles, we expect that there will be microstructure modification even when the 
magnetic field is switched off. Two techniques of microstructure change are proposed. The first technique is that the adsorption 
energy is so strong that the interface is dragged along with the particles until they rejam in their new location and orientation to the 
field. The second technique is that the particles tilt in place out of the interface, causing domain coarsening before the particles jam 
in their new positions and orientations. The mechanism, derived microstructure change and timescales will be assessed in this aim.

The response of bijels to magnetic fields will be assessed through analyzing how model bijels made with no fields respond to field strengths 
above and below the critical field strength as calculated from Bresme Faraudo theory. The microstructure properties such as the average domain 
size, particle orientation to the field and interface and the Steinhardt 6 fold bond order parameter to examine the spatial relationship of 
the particles to their neighbors. These techniques will allow elucidation of which mechanism is present at which magnetic field strength. 
Additionally, the microstructure changes observed will be characterized and compared to one another to assess how the applied magnetic field 
changes the final microstructure obtained.

Next, the importance of the initial order of the particle monolayer will also be assessed through increasing the applied field to equal to the 
surface tension forces on bijel templates simulated under various field strengths. The applied field will also be switched off on bijel templates 
simulated under the same field strengths. The same analysis metrics mentioned earlier will be used. Additionally, the microstructures with the 
same difference in applied field,  will be assessed to investigate the reversibility of bijel microstructures.

@@

In many of the fabrication processes described above, the rheology of the bijel casting mixture is essential. 
\cite{haase_continuous_2015, cai_bijels_2017, amirfattahi_fabrication_2024} Ching showed that rheologically, bijels are 
colloidal glasses percolating in 3D space. \cite{ching_bijel_2022} A shear capillary number, $Ca_s$, is defined that correlates the 
applied strain rate to the capillary forces derived from surface tension. \cite{frijters_effects_2012, yang_capillary_2022} We are interested 
in identifying the effect of the initial microstructure and an applied field on the rheological properties of the bijel.

@@

For this study, the yield stress and viscosity of the bijels will be explored as a function of the initial microstructure under 
various $Ca_s$. The initial microstructure will be derived from bijels stabilized with ellipsoidal particles made with no magnetic field 
and with a field strength equal to the surface tension energy. We then apply constant shear defined with $Ca_s$ to determine the yield stress and non-newtonian
characteristics of the bijel. Previous investigations have revealed that the ordering of particles in the direction of shear change
the rheological behavior significantly compared to unordered systems. Additionally, the domains of the bijel may create additional mechanisms for 
rheological behavior modification which have not been probed in detail yet.

We will then identify the complex rheology of the bijels, calculating the loss and storage modulus of the bijel microstructures detailed earlier
as a function of the oscillation of shear. The loss and storage modulus detail the viscous and elastic behavior of the bijel respectively, meaning 
that the gel point of the bijel can be established as the point when the storage modulus exceeds the loss modulus. We will pay special attention to the 
state of the particles in all simulations, correlating changes in the properties of the particle to observed rheological events. We will also identify if shear banding
is observed.

>>>>

Porous materials are characterized by the presence of pores or voids within their structure, where no solid material is present. 
In contrast, homogeneous materials exhibit a uniform structure devoid of pores. The shape and distribution of these pores can vary, 
and according to the IUPAC classification, materials are categorized based on pore size as microporous ($L < 2$ nm), 
mesoporous ($2 < L < 50$ nm), or macroporous ($L > 50$ nm) \cite{sing_reporting_1985}. The presence of pores significantly 
increases the surface area-to-volume ratio of porous materials compared to their homogeneous counterparts. A commonly used experimental 
technique for estimating the surface area of porous materials, based on Brunauer-Emmett-Teller (BET) theory, has demonstrated that such 
materials can exhibit surface areas more than a hundred times greater than those of homogeneous materials, depending on pore size and pore 
size distribution \cite{shimizu_surface_2022}.

In addition to pore size and its distribution, the spatial arrangement of pores within a material significantly influences its performance, 
often quantified by tortuosity. Tortuosity is defined as the ratio of the actual path length between two points to the Euclidean distance 
between them. A tortuosity greater than one indicates that the path length is longer than the Euclidean distance, whereas a tortuosity less 
than one suggests a more direct pathway. The interplay of these factors has led to the development of a wide range of tailored microstructures 
for diverse applications. Each pore size regime serves distinct functions; for example, microporous materials are commonly used in zeolites and 
photonic bandgap materials, while macroporous materials enhance transport properties, making them suitable for applications such as battery 
electrodes and drug delivery systems \cite{chen_tortuosity_2020, ebner_tortuosity_2014}. The increased surface area-to-volume ratio of porous 
materials further enhances the properties of the base material in various applications, including catalysis, energy storage, and biomedical 
systems, making them important microstructures. \cite{cha_bicontinuous_2019, samdani_bicontinuous_2017, thorson_bijel-templated_2019, zhao_highly_2014}.

@@

Conventionally, porous materials have been synthesized through methods such as solvothermal synthesis and pyrolysis, which are commonly 
used for producing zeolites and activated carbon, respectively. With the increasing demand for tailored porous materials, advanced synthesis 
techniques—including sol-gel synthesis, freeze-drying, and various templating methods—have been developed to fabricate porous structures across 
length scales ranging from $10^{-9}$ m to $10^{-3}$ m 
\cite{stein_morphological_2008, ray_comprehensive_2016, cervellere_mesoscopic_2019, garcia-bennett_unique_2020, zhang_emulsion_2019, alves-rosa_design_2013}. 
Industry has also adopted techniques such as electro-spinning to produce nonwoven fibers, which are widely used in membrane synthesis.  
Among these approaches, templating techniques provide precise control over pore size, enable bottom-up synthesis, and introduce functionality by 
leveraging various physical phenomena. Colloidal templating relies on the close packing of particles to define pore structures. Surfactant and 
polymer templating utilize the self-assembly of macromolecules into their equilibrium configurations to generate porous networks. Emulsion templating, 
on the other hand, exploits the phase separation of partially miscible liquids to form the pore architecture of the resulting material.

Emulsion templating enables the fabrication of porous materials with a wide range of tunable pore sizes, continuous production through microfluidic 
junctions or other flow-based systems, and functionalization through the incorporation of additives or stabilizers. This technique also offers a broad 
scope of accessible microstructures and benefits from mild synthesis conditions. Additionally, it can be extended to generate hierarchical porosity, 
further enhancing the functionality and properties of the resulting materials \cite{yang_hierarchically_2017, thompson_hierarchically_2019, wang_morphology_2023}.  
Figure \ref{fig:bijel_template} illustrates how emulsion templating enables the bottom-up synthesis of hierarchically porous materials, although various 
alternative approaches also exist 
\cite{garcia_scalable_2019, santiago_cordoba_aerobijels_2020, thorson_bijel-templated_2019, lu_controllable_2020, wang_morphology_2023}.

@@

One particularly interesting emulsion-derived microstructure is the bicontinuous interfacially jammed emulsion gel (bijel) 
\cite{stratford_colloidal_2005, herzig_bicontinuous_2007, lee_bicontinuous_2010}. Bijels are formed by arresting the spinodal decomposition of partially 
miscible liquids, a process driven by the adsorption of colloidal particles at the interface. As the interfacial area contracts, the particles become 
jammed, stabilizing the bicontinuous structure, as summarized in Figure \ref{fig:bijel_coarsen}. The resulting co-continuous and tortuous microstructure 
of bijels makes them highly suitable for various porous material applications.

Bijels were first predicted in simulations in 2005 and experimentally realized in 2007 when a mixture of water and 2,6-lutidine, combined with 
surface-modified silica nanoparticles, underwent thermally induced spinodal decomposition \cite{stratford_colloidal_2005, herzig_bicontinuous_2007}. 
Since then, various casting mixtures and particle chemistries have been explored to fabricate bijels using thermally induced spinodal decomposition (TIPS) 
\cite{lee_bicontinuous_2010, bai_dynamics_2015}. More recently, alternative fabrication techniques such as solvent transfer-induced phase separation (STrIPS), 
vapor-induced phase separation (VIPS), non-solvent-induced phase separation (NIPS), homogenization, and liquid-in-liquid printing have been developed. 
These methods enable the continuous synthesis of bijels, making them more suitable for large-scale production 
\cite{haase_continuous_2015, wang_scalable_2020, cai_bijels_2017, yabuno_preparation_2020, wang_bicontinuous_2023, amirfattahi_fabrication_2024}. 
Additionally, these techniques allow for the fabrication of bijels in various shapes and form factors, including fibers, coatings, and capsules, expanding 
their applicability across different fields, as illustrated in Figure \ref{fig:strips} 
\cite{haase_continuous_2015, boakye-ansah_controlling_2020, kharal_hightensile_2020, wang_bicontinuous_2023}.

\begin{figure}[h]
    \centering
    \includegraphics[scale = 2]{figures/literature_review/STRIPPS.jpg}
    \caption{STrIPS in action. Extrusion of the bijel casting mixture into a non-solvent bath, followed by removal of solvent from 
    the casting mixture through diffusion. Reproduced from Haase et al. 2015 under license number 5913140219015. \cite{haase_continuous_2015}}
    \label{fig:strips}
\end{figure}

However, all of these techniques rely on precisely controlling the rate of phase separation, which typically involves adjusting the composition 
of the casting mixture to modify the resulting microstructure. In STrIPS, for example, the bijel microstructure is influenced by both the flow rate 
and the choice of co-solvent, which are selected to regulate the phase separation dynamics \cite{haase_continuous_2015}. These factors directly 
impact material properties such as the mechanical stability of the bijel, which is particularly important in applications like catalysis, where the 
rigidity of the particle monolayer is essential for maintaining consistent performance 
\cite{reeves_particle-size_2015, haase_situ_2016, boakye-ansah_controlling_2020}. Identifying alternative techniques for modifying the microstructure of 
bijels would allow for greater tunability while maintaining the desired composition of the constituent materials. One promising approach for achieving 
such control is the use of stimuli-responsive mechanisms.

@@

Stimuli-responsive mechanisms based on pH, external fields, and temperature have been explored in previous studies to modify the microstructure of emulsion 
droplets for applications such as enhanced oil recovery, pharmaceuticals, and cell adhesion 
\cite{haase_nanoparticle_2011, tham_magnetophoresis_2021, cui_stabilizing_2013, manfredini_limonene--water_2021}. External fields have been shown to 
manipulate emulsion stability, control droplet movement, and induce elongation in emulsion droplets 
\cite{tham_magnetophoresis_2021, cui_stabilizing_2013, melle_pickering_2005}.  
In the case of bijels, spherical particle-stabilized systems subjected to a magnetic field exhibited no significant microstructural changes 
\cite{kim_bijels_2010}. However, bijels stabilized with spherical particles under an electric field demonstrated greater potential for microstructure 
modification \cite{carmack_tuning_2018}. Despite this, magnetic fields present a promising avenue for targeted stimuli-responsive behavior, as even 
weak fields can induce a response while remaining non-invasive in many contexts. This property is particularly advantageous for pharmaceutical and 
bioengineering applications, where external control over material properties is desirable 
\cite{vanoli_bijels_2022, thorson_bijel-templated_2019, thorson_composite_2018}.  
Such applications could benefit from in-situ microstructural modifications, enabling tunable drug delivery rates, improved separations, and enhanced catalyst 
efficiency and permeability. Therefore, developing strategies to modify pore size and tortuosity without requiring the synthesis of a new material would 
significantly expand the functional versatility of bijels.

Anisotropic particles at interfaces have been shown to undergo self-assembly due to the presence of multipolar pressure fields induced by interface 
deformation. Similarly, self-assembly has been observed for ellipsoidal particles at interfaces under magnetic fields. Additionally, ellipsoidal particles 
exhibit magnetic field-controlled orientation at interfaces, as demonstrated by Bresme and Faraudo \cite{bresme_orientational_2007, davies_interface_2014}.  
When subjected to a magnetic field, assemblies of multiple ellipsoidal particles exhibit energy minima at orientations different from those of isolated 
particles. This suggests that the interfacial coverage of surfaces decorated with ellipsoidal particles can be dynamically tuned using external 
stimuli \cite{newton_influence_2014, newton_capillary_2018}. Therefore, ellipsoidal particles at interfaces—whose orientation and packing can be externally 
controlled—present a promising strategy for tailoring the microstructure of bijels.

Bijels offer a bottom-up synthesis approach for porous material templates, enabling scalable and continuous fabrication for both hard and soft material 
applications through STrIPS and related techniques. However, the degree of microstructural control provided by these methods is inherently dependent on 
the composition of the casting mixture. Stimuli-responsive strategies present a means to modify the microstructure of bijels while preserving the 
diverse form factors achievable through continuous synthesis techniques. Previous attempts to induce magnetic stimuli response in bijels stabilized 
with spherical particles have shown limited success \cite{kim_bijels_2010}.

Building on this background, we propose the use of anisotropic particles as a technique to enable microstructure modification of bijels upon the application 
of an external field, both during and after fabrication. This work aims to explore methods for controlling the bijel microstructure independently of the casting 
mixture composition by utilizing magnetic stimuli on bijels stabilized with magnetically responsive ellipsoidal particles.  
The proposed mechanism of microstructure modification is based on the reorientation of particles in response to the applied magnetic field, which alters the 
packing arrangement of the particles at the interface. By modifying the interfacial packing, the point at which the particles jam is also altered, thereby 
affecting the jamming point of the bijel. This mechanism is expected to be effective both during and after the synthesis process. Additionally, the 
processability of bijels produced using this technique will be examined to assess how changes in particle packing influence the rheological properties of 
the material.

@@

The jamming point of a bijel plays a crucial role in determining the resulting microstructure, as demonstrated by previous studies comparing the length scales 
of bijels synthesized with varying particle volume fractions and sizes \cite{jansen_bijels_2011, reeves_particle-size_2015}. Additionally, it has been shown 
that magnetic fields can facilitate the self-assembly of anisotropic particles at interfaces and control the interfacial angle between the particle's axis 
of symmetry and the interface \cite{davies_interface_2014, davies_assembling_2014}. However, on a curved interface with numerous other particles, it remains 
unclear how the orientation of multiple particles in response to the field and their regular arrangement will influence the jamming behavior of the bijel 
\cite{bresme_orientational_2007, davies_interface_2014}.

To evaluate the microstructure obtained upon the application of a field during the formation of the bijel, homogeneous mixtures containing spherical and 
ellipsoidal particles will be subjected to field strengths both above and below the critical field strength. This critical field strength is the threshold 
at which particle orientations to the interface are governed by the applied field, as calculated by Bresme and Faraudo for the particle aspect ratio 
\cite{bresme_orientational_2007, davies_interface_2014}. The range of selected field strengths will provide insight into the mechanisms controlling 
microstructural changes, enabling verification of the hypothesis and identification of the conditions under which the most control over the microstructure 
can be achieved.

The average and directional domain sizes, along with their relationship to tortuosity, will be used to characterize the microstructural properties of the 
resulting bijel. The nematic order parameter and the average interfacial angle will provide insight into how the application of the field influences particle 
ordering, both among the particles and relative to the interface. Finally, the radial distribution function will be employed to assess whether the expected 
orientational changes upon field application affect the packing of particles at the interface.

@@

Particles at the surface of emulsion droplets have been shown to unjam and rejam into new, stable microstructures upon the application of stimuli 
\cite{cui_stabilizing_2013}. Magnetic fields applied to bijels stabilized with ellipsoidal particles will promote the unjamming and rejamming of the 
particle monolayer, leading to modifications in the bijel's microstructure. Due to local changes in the state of the particles—specifically, alterations 
in the interfacial ordering and the direction and arrangement of particles—we anticipate that microstructure changes will persist even after the magnetic 
field is turned off. Two mechanisms for microstructure modification are proposed. The first suggests that the adsorption energy is sufficiently strong to 
cause the interface to move with the particles, allowing them to rejam in new locations and orientations relative to the field. The second mechanism posits 
that the particles tilt within the interface, leading to domain coarsening before jamming in their new positions and orientations. This study will assess the 
mechanism, the resulting microstructural changes, and the associated timescales.

The response of bijels to magnetic fields will be evaluated by analyzing how model bijels, synthesized without applied fields, respond to field 
strengths both above and below the critical field strength, as calculated using Bresme and Faraudo's theory. Microstructural properties, including the 
average domain size, particle orientation relative to the field and interface, and the Steinhardt 6-fold bond order parameter, will be used to examine 
the spatial relationships between particles and their neighbors. These techniques will enable the identification of the mechanisms active at different 
magnetic field strengths. Additionally, the observed microstructure changes will be characterized and compared to assess how the applied magnetic field 
influences the final microstructure.

Next, the importance of the initial ordering of the particle monolayer will be assessed by increasing the applied field to levels equal to the surface 
tension forces on bijel templates simulated under various field strengths. The applied field will also be switched off for bijel templates simulated under 
the same conditions. The same analysis metrics mentioned previously will be used. Additionally, microstructures with the same difference in applied field 
will be examined to investigate the reversibility of bijel microstructures.

@@

In many of the fabrication processes described above, the rheology of the bijel casting mixture plays a crucial role 
\cite{haase_continuous_2015, cai_bijels_2017, amirfattahi_fabrication_2024}. Ching demonstrated that, rheologically, bijels behave as colloidal 
glasses percolating in 3D space \cite{ching_bijel_2022}. A shear capillary number, \( Ca_s \), is defined to correlate the applied strain rate 
with the capillary forces derived from surface tension \cite{frijters_effects_2012, yang_capillary_2022}. This study aims to identify the effect 
of the initial microstructure and applied field on the rheological properties of the bijel.

@@

In this study, the yield stress and viscosity of the bijels will be examined as a function of the initial microstructure under various $Ca_s$ values. 
The initial microstructure will be derived from bijels stabilized with ellipsoidal particles, synthesized both without a magnetic field and with a field 
strength equal to the surface tension energy. Constant shear, defined by $Ca_s$, will be applied to determine the yield stress and non-Newtonian 
characteristics of the bijel. Previous studies have shown that particle ordering in the direction of shear significantly alters the rheological behavior 
compared to unordered systems. Additionally, the domains within the bijel may introduce new mechanisms for modifying rheological properties, which have 
yet to be explored in detail.

We will then investigate the complex rheology of the bijels by calculating the loss and storage moduli of the bijel microstructures described 
earlier as a function of oscillatory shear. The loss and storage moduli describe the viscous and elastic behavior of the bijel, respectively, 
allowing the gel point of the bijel to be determined as the point at which the storage modulus exceeds the loss modulus. Special attention will be 
given to the state of the particles in all simulations, correlating changes in particle properties with observed rheological events. Additionally, 
we will assess whether shear banding occurs.
